### 2015-09-09 poisson_errker.tex
Committing lost work from laptop

\subsection{Fourier Interpretation}

Even though there has been much effort on finding alternate rapidly
convergent series representations of the Green's function (see
e.g. Marshall~\cite{marshall99}), it turns out that the form of the
Green's function given in~\eqref{eq:green}, is ideally suited
for our needs as it allows us to easily express the solution in the
Fourier domain in terms of the Fourier coefficients of $f$.

>>>>

\subsection{Fourier Interpretation}
Even though there has been much effort on finding alternate rapidly convergent series representations of the Green's function (see e.g. Marshall~\cite{marshall99}), it turns out that the form of the Green's function given in~\eqref{eq:green}, is ideally suited for our needs as it allows us to easily express the solution in the Fourier domain in terms of the Fourier coefficients of $f$.
